\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{cancel}
\usepackage{hyperref}
\usepackage{tikz}

\title{Styx and Stones: Level Editing Flow and Architecture}
\author{
    \large
    Devin McGinty\\
    \normalsize
    dlm348@drexel.edu
}

\begin{document}
\maketitle

\tableofcontents
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
Styx and Stones is a 2D platforming game created by the FoodTaste Drexel Senior Project Team consisting of members
\begin{itemize}
    \item \href{mailto:jinu.jacob@drexel.edu}{Jinu Jacob}
    \item \href{mailto:brendan.k.kelley@drexel.edu}{Brendan Kelley}
    \item \href{mailto:bailey.s.myers-morgan@drexel.edu}{Bailey Myers-Morgan}
    \item \href{mailto:dlm348@drexel.edu}{Devin McGinty}
    \item \href{mailto:le.n.nguyen@drexel.edu}{Le Nguyen}
    \item \href{mailto:nicole.m.vecere@drexel.edu}{Nicole Vecere}
\end{itemize}

The purpose of this document is to demonstrate the process of designing levels and loading them into an instance of
the \textsc{Styx and Stones} software program for the user to interact with. In the rest of this document the term
``the game'' refers to the ``\textsc{Styx and Stones}'' game program. The general process is to design the level in the
\href{http://www.mapeditor.org}{\textsc{Tiled} 2D map editor}, make the level file readable in Unity using the
\href{http://www.seanba.com/tiled2unity}{\textsc{Tiled2Unity}} command line tool, and read the file using a C\#
deserializer embedded in the \textsc{Unity} engine.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Architecture}
\subsection{Tiled Map Editor}
\textsc{Tiled} is a free and open source 2D tile-based map editor. \textsc{Tiled} allows the person in the role of
``level designer'' to load in 2D assets and design a level. 2D asset files are formatted as an image file with
individual assets formatted as a bitmapped sprite conforming to a fixed-size grid. \textsc{Tiled} uses an intuitive
drag and drop layer-based interface for level design. \textsc{Styx and Stone} will implement layers as defined below.
Note that these descriptions mention game mechanics that are handled by the game engine in \textsc{Unity}
\begin{description}
    \item[Background] \hfill \\
        These are visuals that the player's character can not interact with. Unless specifically defined, background
        assets will appear behind all other assets.
    \item[Surfaces] \hfill \\
        These are dimensional platforms. Except for certain circumstances, the player can not clip through these
        platforms on collision.. Common types of surfaces are walls and floors.
    \item[Collectibles] \hfill \\
        Collectible objects are drawn when the level is loaded, and disappear when the player collides with them.
        Their purpose is logically defined in the game engine.
    \item[Switches] \hfill \\
        Each switch will have a sprite consisting of two graphics. Switches are toggled by the player's character as
        defined in the game engine. A switch has a boolean value, and the graphic displayed is based on the state of
        this value. Switches are initialized when the level is loaded.
    \item[Other Interactive] \hfill \\
        There may be other interactive elements in the game, including doors and AI-controlled enemies.
\end{description}

Levels designed using \textsc{Tiled} are exported as \texttt{.tmx} files. TMX (Tile Map XML) is a tag-based object
format. A level's TMX file defines the tileset file to use, graphical information about the level, and the layout data
for the level. It should be noted that \textsc{Tiled} is a design tool rather than a development tool. Therefore, it
is not included in the development repository for \textsc{Styx and Stones}.

\subsection{Tiled2Unity Deserialization}
\textsc{Tiled2Unity} is a community-made open source tool for the \textsc{Unity} game development engine.
\textsc{Tiled2Unity} provides deserialization for TMX files to make them readable by \textsc{Unity}. Primitive object
interaction is also defined using \textsc{Tiled2Unity}, including sprite transitions and collisions. The mechanics of
these behaviors are defined in \textsc{Unity}.

\subsection{Unity Game Development Engine}
\textsc{Unity} is cross-platform engine and software development kit for game development. All game logic is defined
within \textsc{Unity}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Loading Levels}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Current Challenges}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

